Genetic Dilution erodes productivity: Exploring farmers' low adoption levels of improved maize in Ethiopia

### 2023-03-20 document/slides/NEUDC 2022/discussant/main.tex
Updates from Overleaf

%------------------------------------------------------------
%This block of code defines the information to appear in the
%Title page
\title[Genetic Dilution in Improved Maize] %optional/
{A Case of Genetic Dilution in Improved Maize: Estimating
Comparative Advantage of Adoption in Ethiopia}

\author[et al]{Aleksandr Michuda\inst{1} \and Cristina Chiarella\inst{2} \and Oscar Barriga-Cabanillas\inst{3} \and Juan Correa\inst{4}}

\institute{\inst{1} Cornell University \and \inst{2} UCLouvain \and \inst{3} World Bank Corp. \and \inst{4} FAO}

@@

\date[November 2022] % (optional)
{NEUDC   \\
November 2022}

@@

%---------------------------------------------------------
\begin{frame}
\frametitle{Introduction}

Food security is a major challenge: Ethiopia is no exception

\begin{itemize}
    % \item Struggled to provide an adequate and reliable food supply
    \item Breakthroughs in maize germplasm ($\uparrow$ yields, $\uparrow$ drought tolerance)
\end{itemize}

However adoption of improved seed has remained a challenge

\begin{enumerate}[ {[}1{]} ]
    \item Market integration
    \item Access to supplementary inputs
    \item Agro-ecological considerations 
    \item Lack of learning \citep{Conley2010-ue}
\end{enumerate}

\end{frame}

\begin{frame}{Research Question}

\textbf{How does misclassification in adoption status mask heterogeneous impacts to adoption?}
\end{frame}

\begin{frame}{Preview of Results}

\begin{enumerate}[ {[}1{]} ]
    \item Explore heterogeneous comparative advantages through GRC: find puzzling results.
    \item Endogenous switching regression with different definitions of improved seeds: self-reported, second generation or recycled, purity of genetic material, year of release, types and source.
    \item Low adoption of newest and purest varieties, which do return in higher yields. 
    \item When we account for misclassification in GRC, the puzzle is resolved
\end{enumerate}
\end{frame}

%---------------------------------------------------------
\begin{frame}
\frametitle{Ethiopian Maize}

\begin{itemize}
    % \item Struggled to provide an adequate and reliable food supply
    \item Use ESS waves 1-4, agricultural questionnaires
    \item Waves 1-3 were a panel and included information on yields, inputs and hybrid maize adoption
    \item Wave 4 is a break from Waves 1-3, but contains similar information $+$ DNA fingerprinting
    \item We focus on maize producing households 
    \item Self-reported use of improved seed varieties
    \item Self-reported yields
\end{itemize}

\begin{figure}
    \centering
    \includegraphics[scale=.4]{results/figures/map_hhids.pdf}
\end{figure}

% \textit{Add interesting image}
\end{frame}

\begin{frame}{}

\begin{figure}
    \centering
    \includegraphics[width=.7\textwidth]{results/figures/adoption_r4.png}
    \caption{Caption}
    \label{fig:my_label}
\end{figure}

\end{frame}

%---------------------------------------------------------
\begin{frame}
\frametitle{Empirical Strategy I: Finding the returns from adoption}

\textbf{Understand the returns of adopting improved varieties: }
\begin{itemize}
    \item Some farmers are ``more suited'' for adoption (comparative advantage) \citep{Suri2011-oi}
    \item How comparative advantage plays a role on using improved seed varieties and its returns.
    \item Use Group Random Coefficient (GrRC) method \citep{Tjernstrom_Emilia_Dalia_Ghanem_Oscar_Barriga_Cabanillas_Travis_J_Lybbert_Jeffrey_D_Michler_and_Aleksandr_Michuda2020-bc}
    \item Can separate returns from those who ``should'' be getting highest returns.
\end{itemize}

% (Suri 2011; Tjernstr\"{o}m et al. 2020; Michler et al. 2019; Barriga et al. 2018)

We estimate a Correlated Random Coefficient Model by way of GrRC estimation:
\vspace{-2em}
\begin{center}
$$
    y_{it}= \delta + \Delta h_{it} + \phi\boldsymbol{\theta_i} h_{it} + \tau_{i} + \boldsymbol{\theta_i} + \epsilon_{it}
$$  
\end{center}

\end{frame}

%---------------------------------------------------------
\begin{frame}
\frametitle{Empirical Strategy}
\begin{enumerate}
    \item Identification does not rely on an IV or propensity to adopt.
    \item Identification similar to \cite{Chamberlain1984-uk}: strict exogeneity
    \item strong assumption, but gives us ability to estimate returns to adoption, as well as \textit{advantage in adopting}
    \item Requires enough variation in ``switcher trajectories'' 
\end{enumerate}

\input{results/tables/traj}
\end{frame}

%---------------------------------------------------------
%---------------------------------------------------------
\begin{frame}
\frametitle{The Puzzle}
% \frametitle{Group Random Coefficients Results}

\begin{figure}
    \centering
    \includegraphics[scale=0.5]{results/figures/theta.png}\label{fig:theta_delta_raw}
\end{figure}

\end{frame}

%---------------------------------------------------------

%---------------------------------------------------------
\begin{frame}
\frametitle{What's going on?}

\begin{itemize}
    \item Negative advantage to adopting
    \item Adopting more associated with less advantage
    \item Negative returns (but that's part of the standard story about access)
\end{itemize}

\end{frame}

\begin{frame}{How do we resolve this puzzle?}
\begin{itemize}
    \item Explore 4th wave
    \item We use the DNA-fingerprinting to shed light on this puzzle
    \item DNA allows us to assess what varieties (and purity) farmers are using, 
    \item We implement an endogenous switching regression approach
\end{itemize}

\end{frame}
%---------------------------------------------------------

%---------------------------------------------------------
\begin{frame}
\frametitle{Endogenous Switching Regression Results}

\begin{table}[H]
\resizebox{.75\textwidth}{!}{
\centering
\hspace*{-1.2cm}
\begin{threeparttable}
\caption{Effects on yields (log) from adopting improved maize varieties (DNA fingerprinting)}
\label{tab:switch2}
\begin{tabular}{l cccccc}
\hline
\hline
            &Adopters yields&Non-adopters yields&         ATE&          SE&     p-value\\
\hline
\textit{DNA 70, SR yields}&            &            &            &            &            \\
ATT         &        7.17&        7.31&      \fcolorbox{red}{lightgray}{-0.14}&       0.026&      0.0000\\
%
%
%
ATU         &        8.76&        6.76&        2.00&       0.036&      0.0000\\
%
%
%
\textit{DNA 90, SR yields}&            &            &            &            &            \\
ATT         &        7.18&        9.07&       \fcolorbox{red}{lightgray}{-1.90}&       0.023&      0.0000\\
%
%
%
ATU         &        7.01&        6.80&        0.21&       0.022&      0.0000\\
%
%
%
\textit{DNA 95, SR yields}&            &            &            &            &            \\
ATT         &        7.30&        7.08&        \fcolorbox{red}{lightgray}{0.22}&       0.036&      0.0000\\
%
%
%
ATU         &        6.87&        6.86&       0.018&       0.029&      0.5496\\
%
%
%
\textit{HYB, SR yields}&            &            &            &            &            \\
ATT         &        7.28&        7.25&       \fcolorbox{red}{lightgray}{0.030}&       0.028&      0.2892\\
%
%
%
ATU         &        7.06&        6.85&        0.21&       0.028&      0.0000\\
%
%
%
\textit{DTMZ, SR yields}&            &            &            &            &            \\
ATT         &        7.42&        6.53&        \fcolorbox{red}{lightgray}{0.89}&       0.074&      0.0000\\
%
%
%
ATU         &        7.11&        7.02&       0.089&       0.022&      0.0001\\
%
%
%
\textit{CGIAR source, SR yields}&            &            &            &            &            \\
ATT         &        7.13&        6.71&        \fcolorbox{red}{lightgray}{0.43}&       0.033&      0.0000\\
%
%
%
ATU         &        9.19&        6.89&        2.31&       0.018&      0.0000\\
%
%
%
\textit{Year 2010+, SR yields}&            &            &            &            &            \\
ATT         &        7.44&        6.92&        \fcolorbox{red}{lightgray}{0.53}&       0.039&      0.0000\\
%
%
%
ATU         &        8.98&        6.91&        2.07&       0.056&      0.0000\\
%
%
%
\hline
\hline
\end{tabular}
\end{threeparttable}
}
\end{table}

\end{frame}
%---------------------------------------------------------

%---------------------------------------------------------
\begin{frame}
\frametitle{Discussion}
Negative and small returns to adoption from self-reported improved varieties.
\begin{itemize}
    \item But positive returns to more genetically pure, DTMZ, CG- sourced and newer varieties.
    \item All DNA fingerprints are 70\% pure or higher. Control group has high share of false positives: no proper  control.  
\end{itemize}

Could misclassification be masking returns heterogeneity?
\begin{itemize}
    \item If farmers using some mix of traditional hybrid maize or using incorrect practices, this would attenuate effects
    \item Trajectories would be misclassified.
\end{itemize}

\end{frame}

\begin{frame}{Misclassification Driving Returns?}
\begin{itemize}
    \item Use a misclassification robust variant of GRC
    \item Maximum likelihood estimation that uses misclassification rates in estimation, inspired by \cite{michuda2021three}
    \item Use Wave 4 misclassification rates for Waves 1-3
\end{itemize}

\begin{equation*}
\label{eq:mr-grc}
l(\mu, \kappa, \Delta, \beta, \sigma|y_{t}, \hat{h}) = \sum_{\underbar{$h$}\in\mathcal{H}} \left[ f_{Y_{t}| \mathcal{H}}(y|h=\underbar{$h$})\cdot  \sum_{\bar{h} \in \mathcal{H}} \boldsymbol{1\{\hat{h}=\bar{h}\} p_{\underbar{$h$}, \bar{h}}} \right]
\end{equation*}

\end{frame}

\begin{frame}{Misclassification Rates from Wave 4}

\begin{itemize}
    \item Use rate of reported hybrid of at least 95\% purity, against genetic fingerprinting to calculate misclassification
    \item Farmer who reports using traditional seed actually using hybrid 14\% of the time
    \item Farmer who reports using hybrid seed is actually using traditional seed almost \textit{30\%} of the time.
\end{itemize}
    \begin{table}[]
        \centering
        \begin{tabular}{lll}
        \toprule
         & 0 & 1 \\
        \midrule
        0 & 0.863 & 0.137 \\
        1 & 0.296 & 0.704 \\
        \bottomrule
        \end{tabular}
    \end{table}

\begin{equation}
    \label{eq:misclass}
    P(h = (i,j,k) , \hat{h} = (\hat{i},\hat{j}, \hat{k})) = p_{i, \hat{i}}\cdot p_{j, \hat{j}}\cdot p_{k, \hat{k}}
\end{equation}
\end{frame}

\begin{frame}{Misclassified GRC Results}

\begin{figure}
    \centering
    \includegraphics[scale=0.4]{results/figures/mr-theta.png}
\end{figure}
\end{frame}

\begin{frame}{Conclusion}

Accounting for misclassification resolves the issue and makes the adoption problem the classic story about access and a lack of profitability.

\begin{itemize}
    \item Misclassification may work through a measurement problem, but also through changes in practices
    \item Mismatch between cultivation practices and seed used
    \item Effects of high-yielding varieties diminish over time, but traditional varieties are well adapted to local agro-ecological conditions.
    \begin{itemize}
    \item There may be a threshold in time above which it may be more profitable to use a traditional variety than an improved one that has been around for too many generations.
    \item Example: 010 trajectory
\end{itemize}
\end{itemize}

\end{frame}

\begin{frame}
Thank you!

\begin{itemize}
    \item I would be happy to discuss any questions and please feel free to email me!
    \item am2497@cornell.edu
\end{itemize}

\end{frame}

>>>>

%------------------------------------------------------------
%This block of code defines the information to appear in the
%Title page
\title{Discussing: "Seeding the Seeds: Role of Social Structure in
Agricultural Technology Diffusion"}

\author[et al]{Alain de Janvry, Manaswini Rao, Elisabeth Sadoulet}

@@

\date[November 2022] % (optional)
{Discussant:\\
Aleksandr Michuda}

@@

%---------------------------------------------------------
\begin{frame}{Short Summary}
    \begin{itemize}
        \item Returning to the site of two-staged randomized experiment in Emerick et al. (2016)
        \item Introduction of flood resistant paddy variety 
        \item Evaluating diffusion of seed from treatment to non-treatment households
        \item Dynamic treatment effects mask heterogeneity found across jati (sub-castes) in regions
        \item Less village-level fractionalization of jati leads to higher levels of diffusion and adoption by non-treatment households
    \end{itemize}
\end{frame}

\begin{frame}{Highlights}
    \begin{itemize}
        \item Compelling story; just as important to look at spillovers as for treatment, itself
        \item Merges two interesting literatures: seed tech. adoption and economics of Indian caste
        \item has clear policy implications for future policy 
        interventions 
        \item In particular, social hierarchy results are very interesting!
    \end{itemize}    
\end{frame}

\begin{frame}{Feedback}
    \begin{itemize}
        \item Regression of Flood x Treatment unclear for untreated households
            \begin{itemize}
                \item Being in more flood-prone areas will increase rate of adoption?
                \item perhaps using lagged treatment would do better?
            \end{itemize}
        \item Why use an indicator for ELF, and not the continuous variable?
        \item In many cases, for a particular year, adoption and area cultivated increases with similar jati rank, or having someone from your jati receive the mini-kit, but the seed source outcome stays insignificant or is only significant in 2015
            \begin{itemize}
                \item The argument in the paper is that this diffusion happens through one's network, however, the lack of results from seed source makes me want a story about mechanisms. How are these seeds being used if not through seed exchange?
                \item If seed is readily available, is this story more about ``information'' exchange than the physical seed?
            \end{itemize}
    \end{itemize}
\end{frame}

\begin{frame}{Feedback}

\begin{itemize}
    \item How often does a treated village also get treated with a flood?
    \item In some cases, I'm inclined to think that the paper might be have power challenges, and whether it might be useful to have a continuous flood measure? Villages that might not have full-on floods, but that are close and observe floods might also be more likely to adopt
\end{itemize}

\textbf{Minor Feedback}
    \begin{itemize}
        \item Why not make all tables into figures as you have for other regressions?
    \end{itemize}
\end{frame}

### 2023-03-20 document/slides/NEUDC 2022/main.tex
Updates from Overleaf

\documentclass{beamer}
\usepackage[utf8]{inputenc}
\usepackage{threeparttable}
%\usepackage{utopia} %font utopia imported

\usepackage{amsthm, booktabs, setspace, natbib, amsfonts,amssymb,epstopdf,textcomp,listings, xcolor}

@@

\author[et al]{Aleksandr Michuda\inst{1} \and Cristina Chiarella\inst{2} \and Oscar Barriga-Cabanillas\inst{3} \and Juan Correa\inst{4}}

\institute{\inst{1} Cornell University \and \inst{2} UCLouvain \and \inst{3} World Bank Corp. \and \inst{4} FAO}

@@

However adoption of improved seed has remained a challenge

\begin{enumerate}[ {[}1{]} ]
    \item Market integration
    \item Access to supplementary inputs
    \item Agro-ecological considerations 
    \item Lack of learning \citep{Conley2010-ue}
\end{enumerate}

@@

\begin{enumerate}[ {[}1{]} ]
    \item Explore heterogeneous comparative advantages through GRC: find puzzling results.
    \item Endogenous switching regression with different definitions of improved seeds: self-reported, second generation or recycled, purity of genetic material, year of release, types and source.
    \item Low adoption of newest and purest varieties, which do return in higher yields. 
    \item When we account for misclassification in GRC, the puzzle is resolved
\end{enumerate}
\end{frame}

@@

\begin{itemize}
    % \item Struggled to provide an adequate and reliable food supply
    \item Use ESS waves 1-4, agricultural questionnaires
    \item Waves 1-3 were a panel and included information on yields, inputs and hybrid maize adoption
    \item Wave 4 is a break from Waves 1-3, but contains similar information $+$ DNA fingerprinting
    \item We focus on maize producing households 
    \item Self-reported use of improved seed varieties
    \item Self-reported yields
\end{itemize}

@@

\begin{figure}
    \centering
    \includegraphics[width=.7\textwidth]{results/figures/adoption_r4.png}
    \caption{Caption}
    \label{fig:my_label}
\end{figure}

@@

%---------------------------------------------------------
\begin{frame}
\frametitle{Empirical Strategy I: Finding the returns from adoption}

\textbf{Understand the returns of adopting improved varieties: }
\begin{itemize}
    \item Some farmers are ``more suited'' for adoption (comparative advantage) \citep{Suri2011-oi}
    \item How comparative advantage plays a role on using improved seed varieties and its returns.
    \item Use Group Random Coefficient (GrRC) method \citep{Tjernstrom_Emilia_Dalia_Ghanem_Oscar_Barriga_Cabanillas_Travis_J_Lybbert_Jeffrey_D_Michler_and_Aleksandr_Michuda2020-bc}
    \item Can separate returns from those who ``should'' be getting highest returns.
\end{itemize}

@@

%---------------------------------------------------------
\begin{frame}
\frametitle{Empirical Strategy}
\begin{enumerate}
    \item Identification does not rely on an IV or propensity to adopt.
    \item Identification similar to \cite{Chamberlain1984-uk}: strict exogeneity
    \item strong assumption, but gives us ability to estimate returns to adoption, as well as \textit{advantage in adopting}
    \item Requires enough variation in ``switcher trajectories'' 
\end{enumerate}

\input{results/tables/traj}
\end{frame}

%---------------------------------------------------------
%---------------------------------------------------------
\begin{frame}
\frametitle{The Puzzle}
% \frametitle{Group Random Coefficients Results}

@@

\begin{frame}{How do we resolve this puzzle?}
\begin{itemize}
    \item Explore 4th wave
    \item We use the DNA-fingerprinting to shed light on this puzzle
    \item DNA allows us to assess what varieties (and purity) farmers are using, 
    \item We implement an endogenous switching regression approach
\end{itemize}

@@

Could misclassification be masking returns heterogeneity?
\begin{itemize}
    \item If farmers using some mix of traditional hybrid maize or using incorrect practices, this would attenuate effects
    \item Trajectories would be misclassified.
\end{itemize}

@@

\begin{frame}{Misclassification Driving Returns?}
\begin{itemize}
    \item Use a misclassification robust variant of GRC
    \item Maximum likelihood estimation that uses misclassification rates in estimation, inspired by \cite{michuda2021three}
    \item Use Wave 4 misclassification rates for Waves 1-3
\end{itemize}

\begin{equation*}
\label{eq:mr-grc}
l(\mu, \kappa, \Delta, \beta, \sigma|y_{t}, \hat{h}) = \sum_{\underbar{$h$}\in\mathcal{H}} \left[ f_{Y_{t}| \mathcal{H}}(y|h=\underbar{$h$})\cdot  \sum_{\bar{h} \in \mathcal{H}} \boldsymbol{1\{\hat{h}=\bar{h}\} p_{\underbar{$h$}, \bar{h}}} \right]
\end{equation*}

@@

\begin{itemize}
    \item Use rate of reported hybrid of at least 95\% purity, against genetic fingerprinting to calculate misclassification
    \item Farmer who reports using traditional seed actually using hybrid 14\% of the time
    \item Farmer who reports using hybrid seed is actually using traditional seed almost \textit{30\%} of the time.
\end{itemize}
    \begin{table}[]
        \centering
        \begin{tabular}{lll}
        \toprule
         & 0 & 1 \\
        \midrule
        0 & 0.863 & 0.137 \\
        1 & 0.296 & 0.704 \\
        \bottomrule
        \end{tabular}
    \end{table}

@@

\begin{frame}{Misclassified GRC Results}

@@

\begin{itemize}
    \item Misclassification may work through a measurement problem, but also through changes in practices
    \item Mismatch between cultivation practices and seed used
    \item Effects of high-yielding varieties diminish over time, but traditional varieties are well adapted to local agro-ecological conditions.
    \begin{itemize}
    \item There may be a threshold in time above which it may be more profitable to use a traditional variety than an improved one that has been around for too many generations.
    \item Example: 010 trajectory
\end{itemize}
\end{itemize}

@@

\begin{frame}
Thank you!

>>>>

\documentclass{beamer}
\usepackage[utf8]{inputenc}
\usepackage{threeparttable}
%\usepackage{utopia} %font utopia imported
\usepackage{amsthm, booktabs, setspace, natbib, amsfonts,amssymb,epstopdf,textcomp,listings, xcolor}

@@

\author[]{Aleksandr Michuda\inst{1} \and Cristina Chiarella\inst{2} \and Oscar Barriga-Cabanillas\inst{3} \and Juan Correa\inst{4}}

\institute[]{\inst{1} Cornell University \and \inst{2} UCLouvain \and \inst{3} World Bank Corp. \and \inst{4} FAO}

@@

However adoption of improved seed has remained a challenge:

\begin{enumerate}[ {[}1{]} ]
    \item Lack of market integration \citep{Carter2014-fm, adejobi2013markets}
    \item Access to supplementary inputs \citep{Byerlee2013-qk, Munshi2004-og}
    \item Adaptation to agro-ecological conditions \citep{Bird2020-nt}
    \item Tech. Transfer Challenges of learning \citep{Conley2010-ue}
\end{enumerate}

@@

\begin{enumerate}[ {[}1{]} ]
    \item Explore heterogeneous comparative advantages through GRrC (reformulation of \cite{Suri2011-oi}): find puzzling results.
    \item Endogenous switching regression with different definitions of improved seeds: self-reported, second generation or recycled, purity of genetic material, year of release, types and source.
    \item Low adoption of newest and purest varieties, which \textit{in fact} return higher yields. 
    \item Due to genetic dilution, all farmers are using improved seed; biasing results
    \item When we account for misclassification in GRrC, the puzzle is resolved
\end{enumerate}
\end{frame}

@@

\begin{itemize}
    % \item Struggled to provide an adequate and reliable food supply
    \item Use ESS waves 1-4, agricultural questionnaires
    \item Waves 1-3 were a panel and included information on yields, inputs and hybrid maize adoption
    \item Wave 4 is a break from Waves 1-3, but contains similar information $+$ DNA fingerprinting
    \item We focus on maize producing households 
    \item Self-reported use of improved seed varieties and yields
\end{itemize}

@@

\begin{figure}
    \centering
    \includegraphics[width=.7\textwidth]{results/figures/adoption_r4.png}
    \caption{Seed varieties: Adoption rate of improved seed varieties in 2018 (by self-report, purity level, crop type, source and year of release)}
\end{figure}

@@

%---------------------------------------------------------
\begin{frame}
\frametitle{Empirical Strategy}

\textbf{Understand the returns of adopting improved varieties: }
\begin{itemize}
    \item Some farmers are ``more suited'' for adoption (comparative advantage) \citep{Suri2011-oi}
    \item How comparative advantage plays a role on using improved seed varieties and its returns.
    \item Use Group Random Coefficient (GrRC) method \citep{Tjernstrom_Emilia_Dalia_Ghanem_Oscar_Barriga_Cabanillas_Travis_J_Lybbert_Jeffrey_D_Michler_and_Aleksandr_Michuda2020-bc} to  separate returns from those who ``should'' be getting highest returns.
\end{itemize}

@@

%---------------------------------------------------------
\begin{frame}
\frametitle{Empirical Strategy}
\begin{enumerate}
    \item Identification does not require IV
    \item Identification similar to \cite{Chamberlain1984-uk}: strict exogeneity
    \item Strong assumption, but gives us ability to estimate returns to adoption, as well as \textit{advantage in adopting}
    \item Requires enough variation in ``switcher trajectories'' 
\end{enumerate}
\end{frame}

\begin{frame}{Trajectories}
\input{results/tables/traj}

%---------------------------------------------------------
%---------------------------------------------------------
\begin{frame}
\frametitle{The Puzzle: Using high yield varieties does not improved returns}
% \frametitle{Group Random Coefficients Results}

@@

\begin{frame}{How do we resolve this puzzle?}
\begin{itemize}
    \item Use the  4th wave of the survey to leverage DNA-fingerprinting information 
    \item DNA allows us to assess what varieties (and purity) farmers are in reality planting  
    \item We implement an endogenous switching regression approach to properly measure yield return 
    \item Assess the genetic purity of improved varieties, year of release, types and sources
\end{itemize}

@@

Could misclassification be masking returns heterogeneity?
\begin{itemize}
    \item If farmers using genetically diluted hybrid, or older generations, this would attenuate effects
    \item Trajectories would be misclassified.
\end{itemize}

@@

\begin{frame}{Misclassification Driving Returns?}
\begin{itemize}
    \item We estimate a misclassification robust GRrC 
    \item A Maximum likelihood estimation approach uses misclassification rates to properly estimate coefficients on the returns from adoption of high yield varieties $-$inspired by \cite{michuda2021three}
    \item We apply wave 4 misclassification rates for waves 1-3
\end{itemize}

\begin{equation*}
\label{eq:mr-GRrC}
l(\mu, \kappa, \Delta, \beta, \sigma|y_{t}, \hat{h}) = \sum_{\underbar{$h$}\in\mathcal{H}} \left[ f_{Y_{t}| \mathcal{H}}(y|h=\underbar{$h$})\cdot  \sum_{\bar{h} \in \mathcal{H}} \boldsymbol{1\{\hat{h}=\bar{h}\} p_{\underbar{$h$}, \bar{h}}} \right]
\end{equation*}

@@

\begin{itemize}
    \item Use rate of hybrid of at least 95\% purity, against self-reported hybrid use to calculate misclassification
    \item A farmer who reports using traditional seed is actually using hybrid 14\% of the time
    \item A farmer who reports using hybrid seed is actually using traditional seed almost \textit{30\%} of the time.
\end{itemize}
    \begin{table}[]
        \centering
        \begin{tabular}{lll}
        \toprule
         & 0 & 1 \\
        \midrule
        0 & 0.863 & 0.137 \\
        1 & 0.296 & 0.704 \\
        \bottomrule
        \end{tabular}
        \caption{Misclassification Matrix of 95\% genetic purity}
    \end{table}

@@

\begin{frame}{Misclassified GRrC Results}

@@

\begin{itemize}
    \item Farmers think they're adopting improved seed varieties but evidence shows considerable dilution and varieties are not yielding as expected
    \item Misclassification biases estimates through measurement problem, but also through changes in practices
    \item Mismatch between cultivation practices and seed variety used
    \item Effects of high-yielding varieties diminish over time, but traditional varieties are well adapted to local agro-ecological conditions.
    \begin{itemize}
    \item There may be a threshold in time above which it may be more profitable to use a traditional variety than an improved one that has been around for too many generations.
    \item Example: 010 trajectory
\end{itemize}
\end{itemize}

@@

\begin{frame}
\textbf{Thank you!}
